Cost-Benefit Analysis

### 2023-05-12 workflow/notebooks/cost-benefit-analysis.Rmd
Note Krishna's comment re: fidaxomicin
Move most notes to Zotero

- use values from confusion matrix for one representative model on a test set.
  - Number needed to screen (NNS) - the number of alerted patients the models must flag to identify 1 true positive. 
  - Number needed to treat (NNT) - the number of true positive patients one must treat for 1 patient to benefit from the treatment.
  - Number needed to benefit (NNB = NNS x NNT) - how many patients must be screened for 1 patient to benefit.
- assumptions
  - cost of a non-severe case
  - cost of a severe case
    - days in icu, colectomy
  - cost of possible treatments:
    - abx: metronizadole, vancomycin, fidaxomycin
    - fmt, bezlotoxumab (monoclonal antibodies)

@@

- Vince: consider bezlotoxumab since it targets the toxin, mouse models show it reduces organ damage.
- Krishna: bezlotoxumab clinical trials didn't find signal for limiting severity.

### [Gupta _et al.](https://journals.sagepub.com/doi/10.1177/17562848211018654)

@@

### [fidaxomycin clinical trial](https://www.nejm.org/doi/full/10.1056/nejmoa0910812)

no significant difference in whether CDI was cured, but did have significant
difference in recurrence.

### [severe CDI treatment options](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3088840/)

**from 2008, now out of date**

see table for different treatment recommendations for mild-moderate CDI, 
IDSA severe CDI, and complicated CDI.

could compare cost-benefit analysis with IDSA severity.

### [idsa treatment guidelines comparison](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9780550/)

i may need to also consider "fulminant" cdi criteria

### [mich med treatment guidelines](https://www.med.umich.edu/1info/FHP/practiceguides/InptCDiff/C-Diff.pdf)

from 2019, has this been updated?

>>>>

- use values from confusion matrix for one representative model on a test set. or get average precision?
  - Number needed to screen (NNS) - the number of alerted patients the models must flag to identify 1 true positive. 
  - Number needed to treat (NNT) - the number of true positive patients one must treat for 1 patient to benefit from the treatment.
  - Number needed to benefit (NNB = NNS x NNT) - how many patients must be screened for 1 patient to benefit.
- assumptions
  - cost of a non-severe case
  - cost of a severe case
    - days in icu, colectomy
  - cost of possible treatments:
    - abx: metronizadole, vancomycin, fidaxomycin
    - fmt, bezlotoxumab (monoclonal antibodies)

@@

- Vince: consider bezlotoxumab since it targets the toxin, mouse models show it reduces organ damage.
- Krishna: bezlotoxumab clinical trials didn't find signal for limiting severity. however fidaxomicin is superior to vancomycin for cure and time to resolution of diarrhea ([IDSA 2021 update](https://doi.org/10.1093/cid/ciab549)).

### [Gupta _et al._ 2021 - Economic Burden of CDI](https://journals.sagepub.com/doi/10.1177/17562848211018654)

@@
